How Kids Code and How We Know:\\An Exploratory Study on the Scratch Repository

### 2016-04-20 Paper/paper.tex
added reference to example for indentation

We ran Kragle on March 2nd 2016 and let it running for 24 hours, when it had obtained a little over 250.000 programs.  Out of the \nPrograms~, we failed to analyze 2.367 programs due to various technical difficulties \todo{add details, I will check a few to see what went wrong - Felienne}

Kragle, as well as all scraped programs and our analysis files are available\footnote{\url{https://github.com/ScratchLover42/ICER-Data-Code}}.

@@

In Table \ref{tbl-size} we summarize statistics for metrics related to size and complexity. We use the mean value and the five-number summary to describe the dataset in terms of the number of sprites with code per project (including the stage sprite) and the number of scripts per project, where each script is a code-block of interconnected Scratch blocks. For example, in Figure \ref{fig:ui} the cat sprite contains two scripts. We further measure the lines of code per project, considering each Scratch block to represent exactly one line of code, thus not counting the closing constructs of loops or conditional statements as separate lines. The maximum code indentation level is used as a code complexity metric. It was calculated using the JSON array depth? \todo{felienne, how did we measure this?}. This corresponds to code indentation level returning 1 for all first-level blocks and increasing by 2 for block enclosures in loops or conditional statements. Figures \ref{fig:size-sprites}, \ref{fig:size-scripts}, \ref{fig:size-locs} and \ref{fig:size-indent} plot the distribution of those size metrics.

>>>>

We ran Kragle on March 2nd 2016 and let it running for 24 hours, when it had obtained a little over 250.000 programs.  Out of the \nPrograms~, we failed to parse and further analyze 2.367 programs due technical difficulties with the provided JSON files. Kragle, as well as all scraped programs and our analysis files are available\footnote{\url{https://github.com/ScratchLover42/ICER-Data-Code}}.

@@

In Table \ref{tbl-size} we summarize statistics for metrics related to size and complexity. We use the mean value and the five-number summary to describe the dataset in terms of the number of sprites with code per project (including the stage sprite) and the number of scripts per project, where each script is a code-block of interconnected Scratch blocks. For example, in Figure \ref{fig:ui} the cat sprite contains two scripts. We further measure the lines of code per project, considering each Scratch block to represent exactly one line of code, thus not counting the closing constructs of loops or conditional statements as separate lines. Furthermore, we measure the nestedness of program, which is the number of times blocks are placed within each other. For example, the program in Figure \ref{fig:ui} has a maximum indentation of 3 in the `Wgen Green flag clicked' script, as that has a broadcast block within an if, within a forever\todo{for Felienne: double check}. Figures \ref{fig:size-sprites}, \ref{fig:size-scripts}, \ref{fig:size-locs} and \ref{fig:size-indent} plot the distribution of those size metrics.
